Kaggle-in-class Data Challenges Can Boost Student Learning

### 2018-12-20 submission1/paper-kaggle.Rmd
preparing for revision

# to produce blinded version set to 1
blinded: 0

@@

@@

The experiment was conducted during Semester 2 2017. Data was collected during two classes, one at the University of Melbourne (MAST90083), and one at Monash University (ETC2420/5242).

@@

ETC2420/5242, titled Statistical Thinking, covers regression, and has a mix of undergraduate and postgraduate students. Only the 34 postgraduate (5242) students were required to participate in the kaggle competition, and competed in the regression (R) challenge. This was run independently from the University of Melbourne competition. The 145 undergraduate (2420) students were used as controls for examining performance of the postgraduate students. The competition ran for one month. Students formed their own teams of 2-4 members to compete. 
<!--
Several undergraduates also chose to compete individually. The material on regression methods, particularly the computational methods needed to successfully predict housing prices was new to both groups of students. 
-->
<!--
ETC3250, called Business Analytics, is an undergraduate course focusing on data mining. All students participated in a kaggle competition on the classification challenge. Because this group had no comparison group, it was difficult to assess performance. 
-->

@@

This project (title: Effect of Data Competition on Learning Experience) has been approved by the Faculty of Science Human Ethics Advisory Group University of Melbourne (ID: 1749858.1 on September 4, 2017) and by Monash University Human Research Ethics Committee (ID: 9985 on August 24, 2017).

This document was produced in R [@R] with the package knitr [@knitr]. Data cleaning was conducted using tidyr [@tidyr], dplyr [@dplyr] and plots were made with ggplot2 [@ggplot2]. The materials to reproduce the work are available at https://github.com/dicook/paper-quoll.

Information on setting up a Kaggle InClass challenge can be found at https://www.kaggle.com/about/inclass/overview.

>>>>

# to produce blinded version set to 1
blinded: 1

@@

header-includes:
    - \usepackage{setspace}\doublespacing

@@

The experiment was conducted during Semester 2 2017. Data was collected during two classes, one at the University of AB (MAST90083), and one at CD University (ETC2420/5242).

@@

ETC2420/5242, titled Statistical Thinking, covers regression, and has a mix of undergraduate and postgraduate students. Only the 34 postgraduate (5242) students were required to participate in the kaggle competition, and competed in the regression (R) challenge. This was run independently from the University of AB competition. The 145 undergraduate (2420) students were used as controls for examining performance of the postgraduate students. The competition ran for one month. Students formed their own teams of 2-4 members to compete. 
<!--
Several undergraduates also chose to compete individually. The material on regression methods, particularly the computational methods needed to successfully predict housing prices was new to both groups of students. 
-->
<!--
ETC3250, called Business Analytics, is an undergraduate course focusing on data mining. All students participated in a kaggle competition on the classification challenge. Because this group had no comparison group, it was difficult to assess performance. 
-->

@@

This project (title: Effect of Data Competition on Learning Experience) has been approved by the Faculty of Science Human Ethics Advisory Group University of AB (ID: 1749858.1 on September 4, 2017) and by CD University Human Research Ethics Committee (ID: 9985 on August 24, 2017).

This document was produced in R [@R] with the package knitr [@knitr]. Data cleaning was conducted using tidyr [@tidyr], dplyr [@dplyr] and plots were made with ggplot2 [@ggplot2]. The materials to reproduce the work are available at https://github.com/XXX.

<!--
https://github.com/dicook/paper-quoll. 
-->
Information on setting up a Kaggle InClass challenge can be found at https://www.kaggle.com/about/inclass/overview.
